---
title       : NBA team statistics 2013-14
subtitle    : A Shiny app
author      : Ted Quinn
job         : Developing Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Basic description

This document describes a [Shiny app](https://tcquinn.shinyapps.io/nbateamstats/) that allows the user to explore team statistics from the United States National Basketball Association (NBA) 2013-14 regular season. The user selects an $x$ variable and a $y$ variable from among 11 different team statistics (see following page). The app then displays charts summarizing each variable individually and the relationship between the two variables.


--- .class #id 

## Variables

The user chooses an $x$ variable and a $y$ variable from among 11 different team statistics:

* Rebounds per game
* Assists per game
* Steals per game
* Turnovers per game
* Points per game
* Opponent rebounds per game
* Opponent assists per game
* Opponent steals per game
* Opponent turnovers per game
* Opponent points per game
* Win-loss percentage

--- .class #id 

## Summary of individual statistics

The app then produces two sets of charts. The first set of charts summarizes each of the selected statistics with a histogram. The mean of each is marked with a dotted line.
```{r,echo=FALSE,fig.width=10}
source("NBA team stats 2013-14.R")
xcolnum=6
ycolnum=12
xcolname=columnnames[xcolnum]
ycolname=columnnames[ycolnum]
xdata <- data[,xcolnum]
ydata <- data[,ycolnum]
par(mfrow=c(1,2))
hist(xdata,main=NULL,xlab=xcolname,ylab="Number of teams")
abline(v=mean(xdata),lty=2,lwd=2)
hist(ydata,main=NULL,xlab=ycolname,ylab="Number of teams")
abline(v=mean(ydata),lty=2,lwd=2)
```

--- .class #id 

## Relationship between the statistics

The second set of charts summarizes the relationship between the selected statistics with a scatterplot. The standard regression line is marked with a dotted line.
```{r,echo=FALSE,fig.width=10}
source("NBA team stats 2013-14.R")
xcolnum=6
ycolnum=12
xcolname=columnnames[xcolnum]
ycolname=columnnames[ycolnum]
xdata <- data[,xcolnum]
ydata <- data[,ycolnum]
lmfit <- lm(ydata ~ xdata)
plot(xdata,ydata,xlab=xcolname,ylab=ycolname)
abline(lmfit,lty=2,lwd=2)
```


